Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-07-06 paper/ms.tex
either -> any since cooling will occur after formation of the hybrid WD regardless which SNIa progenitor channel (if any) it is in.

In either {\color{red}ANY} case, the hybrid WD will experience a period of cooling, 
which will reduce the stabilizing temperature gradient (the O-Ne layer is hotter 
than the C-O core) and allow the unstable composition gradient to drive 
thermocompositional convection~\citep{brooksetal2017,schwabgaraud2019}.
In the case of the
hybrid WD accreting and approaching the Chandrasekhar mass, accretion will
heat the core and start C fusion, leading to a period of ``simmering" prior
to the explosion, also mixing the interior \citep{PiroBild08}. The upshot is 
that there is likely to be considerable mixing after the hybrid forms that will 
homogenize the composition \citep{denissenkovetal2015,brooksetal2017,schwabgaraud2019}.

>>>>

In any case, the hybrid WD will experience a period of cooling,
which will reduce the stabilizing temperature gradient (the O-Ne layer is hotter 
than the C-O core) and allow the unstable composition gradient to drive 
thermocompositional convection~\citep{brooksetal2017,schwabgaraud2019}.
In the case of the
hybrid WD accreting and approaching the Chandrasekhar mass, accretion will
heat the core and start C fusion, leading to a period of ``simmering" prior
to the explosion, also mixing the interior \citep{PiroBild08}. The upshot is 
that there is likely to be considerable mixing after the hybrid forms that will 
homogenize the composition \citep{denissenkovetal2015,brooksetal2017,schwabgaraud2019}.
